Mean and variance functions used to simulate Gaussian data

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))
wflow_publish("gaussian_signals.Rmd")

## Generate the ground-truth signals

@@

## Plot the signal means

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
		  nrow = 4,ncol = 2)
```

## Plot the signal variances

>>>>

Generate the ground-truth signals
---------------------------------

@@

Plot the signal means
---------------------

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
theme_set(theme_cowplot())
plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
		  nrow = 4,ncol = 2)
```

Plot the signal variances
-------------------------
